MapReduce to My Ears\\ {\Large Using Big Data for Music Synthesis}

### 2013-05-10 writeup/paper.tex
small changes.

The big data revolution has revolutionized the way we think about,
design, and implement algorithms at scale.  As such, problems from all
different areas of computer science have been lifted into the
MapReduce framework.  While MapReduce has been applied to many
large-scale data processing domains, it has been used relatively less
to explore art or creative tasks.  Our project looks to answer: what
kinds of art can we create harnessing large amounts of data at scale?

We present a system to synthesize music using large amounts of data.
The input is a large corpus of images, which is subsequently processed
by our system, and the result is a musical score.  We then mix and
listen to the music.

>>>>

Big data has revolutionized the way we think about, design, and
implement algorithms at scale.  As such, problems from all different
areas of computer science have been lifted into the MapReduce
framework.  While MapReduce has been applied to many large-scale data
processing domains, it has been used relatively less to explore art or
creative tasks.  Our project looks to answer: what kinds of art can we
create harnessing large amounts of data at scale?

We present a system to synthesize music using large amounts of data.
The input is a large corpus of images, which is subsequently processed
by our system, and the result is a musical score.  We then mix,
listen, and refine the algorithm to produce art.
